PubCrawl: A Publication Search Engine

### 2012-05-18 report/paper.tex
Fix some typos

Figures \ref{relevance2} shows the relevance ratio across all search engines.
Relevance ratio is defined as $(H + M) / N$, where $H$ is the number of Highly
Relevant results, $M$ is the number of Moderately Relevant results, and $N$ is
the number of Not relevant results. PubCrawl has relevance ratio comparable to
Google Scholar and Microsoft Academic Search. CiteSeer, on the other hand, has
very poor relevance score since it produces a large number of irrelevant
results. ACM Digital Library has the largest number of relevant documents in
its results.

>>>>

Figure \ref{relevance2} shows the relevance ratio across all search engines.
Relevance ratio is defined as $(H + M) / N$, where $H$ is the number of Highly
Relevant results, $M$ is the number of Moderately Relevant results, and $N$ is
the number of Not relevant results. PubCrawl has relevance ratio comparable to
Google Scholar and Microsoft Academic Search. \citeseer, on the other hand, has
very poor relevance score since it produces a large number of irrelevant
results. ACM Digital Library has the largest number of relevant documents in
its results.
